---
title: "Model comparison between Chi-Squared and Beta Model"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(doMC)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(readr)
library(eulerr)
library(qqman)

registerDoMC(4) # Set number of cores here for parallel processing

donors <- c('CTRL-NEUHE723FGT-02545-G', 'CASE-NEUFV237VCZ-01369-G', 'CTRL-NEUHE723FGT-02545-G', 'CASE-NEUFV237VCZ-01369-G')
rbps = c("24a-hNIL-control-tdp", "24a-hNIL-c9-tdp", "24a-hNIP-control-tdp", "24a-hNIP-c9-tdp")

input_files <- paste0("../data/",rbps, "_input_allelic.out")
ip_files <- paste0("../data/",rbps, "_ip_allelic.out")
filtered_input_files <- str_replace(input_files, "out$", "10readsInput_filtered_epsilon0.3_sharedhet.txt")

sample_index <- 'CTRL-NEUHE723FGT-02545-G'
rbp = "24a-hNIL-control-tdp"
epsilon = 0.3
input_file <- input_files[1]
ip_file <- ip_files[1]
filtered_input_file <- str_replace(input_file, "out$", "10readsInput_filtered_epsilon0.3_sharedhet.txt")
#input <- read_tsv(input_file)


ip_files <- c('/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIL-control-tdp/allelic/24a-hNIL-control-tdp_ip_allelic.out',
 '/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIL-c9-tdp/allelic/24a-hNIL-c9-tdp_ip_allelic.out',
 '/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIP-control-tdp/allelic/24a-hNIP-control-tdp_ip_allelic.out',
 '/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIP-c9-tdp/allelic/24a-hNIP-c9-tdp_ip_allelic.out')

filtered_input_files <- c("/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIL-control-tdp/allelic/24a-hNIL-control-tdp_input_allelic.10readsInput_filtered_epsilon0.3_sharedhet.txt",
                          "/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIL-c9-tdp/allelic/24a-hNIL-c9-tdp_input_allelic.10readsInput_filtered_epsilon0.3_sharedhet.txt",
                          "/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIP-control-tdp/allelic/24a-hNIP-control-tdp_input_allelic.10readsInput_filtered_epsilon0.3_sharedhet.txt",
                          "/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIP-c9-tdp/allelic/24a-hNIP-c9-tdp_input_allelic.10readsInput_filtered_epsilon0.3_sharedhet.txt")


donors <- c('CTRL-NEUHE723FGT-02545-G', 'CASE-NEUFV237VCZ-01369-G', 'CTRL-NEUHE723FGT-02545-G', 'CASE-NEUFV237VCZ-01369-G')
rbps = c("24a-hNIL-control-tdp", "24a-hNIL-c9-tdp", "24a-hNIP-control-tdp", "24a-hNIP-c9-tdp")
bqtls_beta_files <- paste0(dirname(filtered_input_files),'/',
                          rbps,
                          '_beta_10readsInput_filtered_epsilon0.3_ipreads30_allhet_struct_with_peaks.tsv.gz')
                          #'_beta_filtered_epsilon0.3_ipreads30_struct_with_peaks.tsv.gz')
bqtls_betas <- lapply(bqtls_beta_files, read_tsv)
```


## Run chi-squared tests to test if the distribution of alt and ref counts are the same between the two groups (IP and input) or different
```{r}
chisq_files <- paste0(dirname(filtered_input_files),'/', rbps,  '_chisq_results.txt')
all_chisq <- lapply(chisq_files, data.table::fread)
```

```{r}
chisq_files <- paste0(dirname(filtered_input_files),'/',
                      rbps, 
                      '_chisq_results.txt')
all_chisq <- lapply(1:length(rbps), function(j) {
    chisq = foreach(i = 1:nrow(bqtls_betas[[j]]), .combine = bind_rows) %dopar% {
        here = bqtls_betas[[j]][i,]
        input_ref_count <- here$refCount_input
        input_alt_count <- here$altCount_input
        IP_ref_count <- here$refCount_IP
        IP_alt_count <- here$altCount_IP
    
        contingency_table <- matrix(c(input_ref_count, input_alt_count, IP_ref_count, IP_alt_count), 
                                     nrow = 2, 
                                     byrow = TRUE,
                                     dimnames = list(c("Input", "IP"), c("Ref", "Alt")))
    
        # Perform chi-squared test
        chi_square_result <- chisq.test(contingency_table)
        
        # Calculate proportions in each group
        prop_input <- input_ref_count / (input_ref_count + input_alt_count)
        prop_IP <- IP_ref_count / (IP_ref_count + IP_alt_count)
        
        # Calculate log ratio of proportions
        log_ratio_prop <- log10(prop_IP) - log10(prop_input)
        
        with(chi_square_result, tibble(statistic, parameter, p.value, lor = log_ratio_prop))
    }
    
    chisq$q.value = p.adjust(chisq$p.value, method = 'fdr')
    write_tsv(chisq, chisq_files[j])
    return(chisq)
})

```

## Visualizing significant hits from each model
```{r}
for (j in 1:length(rbps)) {
    bqtls_beta <- bqtls_betas[[j]]
    chisq <- all_chisq[[j]]
    for (qthresh in c(0.05)) {
        p1 <- ggplot(bqtls_beta, aes(x = asb_loc, y = ase_loc)) +
            geom_point(data=filter(bqtls_beta,asb_q >= qthresh), color='black')+
            geom_point(data=filter(bqtls_beta,asb_q < qthresh), color='#36ba59') +
            labs(x = "ASB effect size", y = "ASE effect size", title = str_glue("{sum(bqtls_beta$asb_q < qthresh)} SNPs with q < {qthresh} | beta model for {rbps[j]}"))
        p2 <- ggplot(bqtls_beta, aes(x = asb_loc, y = ase_loc)) +
            geom_point(data=bqtls_beta[chisq$q.value >= qthresh,], color='black')+
            geom_point(data=bqtls_beta[chisq$q.value < qthresh,], color='#36ba59') +
            labs(x = "ASB effect size", y = "ASE effect size", title = str_glue("{sum(chisq$q.value < qthresh)} SNPs with q < {qthresh} | chi squared model for {rbps[j]}"))
        print(p1)
        print(p2)
    }
}
```


## How many significant hits are in peaks?
```{r}
qthresh = 0.05
x = bqtls_beta[bqtls_beta$asb_q < qthresh,]
y = bqtls_beta[chisq$q.value < qthresh,]
x_idx = x$in_peak == 1
y_idx = y$in_peak == 1
cat(sum(x_idx)%>%paste0(" out of ", nrow(x), " ", round(sum(x_idx)/nrow(x)*100,3), "% of variants in peaks under chi-squared model"), "\n")
cat(sum(y_idx)%>%paste0(" out of ", nrow(y), " ", round(sum(y_idx)/nrow(y)*100,3), "% of variants in peaks under beta model"), "\n")
cat(paste0(
        length(intersect(x$variantID, y$variantID)), " ",
        length(union(x$variantID, y$variantID)), " ",
        round(length(intersect(x$variantID, y$variantID))/ length(union(x$variantID, y$variantID))*100,  3),
        "% of variants in common between the two models"
      ), '\n')
```

## Shared rbQTLs Venn-diagram (looking across all 4 samples)

```{r}
bqtls_betas%>%lapply(function(x) x$variantID)%>%
  `names<-`(rbps)%>%
  venn%>%
  plot
```

## Manhattan plots across all 4 conditions for both models
```{r}
for (j in 1:length(bqtls_betas)) {
    bqtls_beta <- bqtls_betas[[j]]
    manhattan_plot <- manhattan(data.frame(CHR = bqtls_beta$chrom%>%str_extract("[0-9]+")%>%as.integer, 
                                           BP = bqtls_beta$position,
                                           SNP = bqtls_beta$variantID,
                                           P = bqtls_beta$asb_q), main = paste0(rbps[j], "beta model"))
    print(manhattan_plot)
    manhattan_plot <- manhattan(data.frame(CHR = bqtls_beta$chrom%>%str_extract("[0-9]+")%>%as.integer, 
                                           BP = bqtls_beta$position,
                                           SNP = bqtls_beta$variantID,
                                           P = all_chisq[[j]]$q.value), main = paste0(rbps[j], "Chi-squared model"))
    print(manhattan_plot)
}


```


## Further investigation into where significant hits between two models vary

```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  qthresh = 0.05
  in_chi_sq <- chisq$q.value < qthresh
  in_beta  <- bqtls_beta$asb_q < qthresh
  idx <- !in_chi_sq & in_beta
  p1 = ggplot(bqtls_beta, aes(x = asb_loc, y = ase_loc, text = variantID)) +
   geom_point(data=bqtls_beta[!idx,], color='black')+
   geom_point(data=bqtls_beta[idx,], color='#36ba59') +
   labs(x = "ASB effect size", y = "ASE effect size", title = str_glue("{sum(idx)} SNPs with q < {qthresh} in beta but not in chi-sq model q < {qthresh}"))
  idx <- in_chi_sq & !in_beta
  p2 = ggplot(bqtls_beta, aes(x = asb_loc, y = ase_loc, text = variantID)) +
   geom_point(data=bqtls_beta[!idx,], color='black')+
   geom_point(data=bqtls_beta[idx,], color='#36ba59') +
   labs(x = "ASB effect size", y = "ASE effect size", title = str_glue("{sum(idx)} SNPs with q < {qthresh} in chi squared model but not in beta model q < {qthresh}"))
  print(p1)
  print(p2)
}
```


```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  idx <- !in_chi_sq & in_beta
  cat(rbps[j],'\n')
  cat(sum(idx), ' in beta and not in chi-squared\n')
  idx <- in_chi_sq & !in_beta
  cat(sum(idx), ' in chi-squared and not in beta\n')
  cat("\n-------------------------------------------\n")
}
```


In 24a-hNIP-c9-tdp, rs33943686 looks like it's right before a junction and upstream of a peak. This was found by chi-squared but not by the beta model.

In 24a-hNIP-c9-tdp, looks like it's right before a junction and upstream of a peak

## High-effect-size hits that align between two models:
```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.01
  in_beta  <- bqtls_beta$asb_q < 0.01
  idx <- in_chi_sq & in_beta & abs(bqtls_beta$asb_loc) > 1.3
  cat(rbps[j],'\n')
  cat(paste(bqtls_beta$variantID[idx], collapse = "\n"))
  cat("\n-------------------------------------------\n")
}
```
## From 24a-hNIL-control-tdp rs56264956, found by beta model and not by chi-squared model is somewhat near a peak

```{r}
bqtls_betas[[1]]%>%filter(variantID == "rs56264956")
```

## How many SNPs are in peaks?

### Look at overlap of these between the models and between the samples
```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.01
  in_beta  <- bqtls_beta$asb_q < 0.01
  cat(rbps[j],'\n')
  idx <- in_chi_sq & !in_beta & bqtls_beta$in_peak
  cat(sum(idx), ' in peaks chi sq only\n')
  idx <- in_beta & !in_chi_sq & bqtls_beta$in_peak
  cat(sum(idx), ' in peaks beta only\n')
  idx <- in_beta & in_chi_sq & bqtls_beta$in_peak
  cat(sum(idx), ' in peaks both\n')
  cat("\n-------------------------------------------\n")
}
```

```{r}
for (j in 1:length(bqtls_betas)) {
bqtls_beta <- bqtls_betas[[j]]
chisq <- all_chisq[[j]]
in_chi_sq <- chisq$q.value < 0.05
in_beta  <- bqtls_beta$asb_q < 0.05
group <- rep('', nrow(bqtls_beta))
group[!in_chi_sq & !in_beta] <-  "Not significant"
group[in_chi_sq & !in_beta] <- "Significant in Chi-Squared Model only"
group[!in_chi_sq & in_beta] <-  "Significant in Beta Model only"
group[in_chi_sq & in_beta] <-  "Significant in both models"
# Plotting input ratio vs IP ratio and seeing if it’s called a bqtl by one model, another, or both
p <- ggplot(bqtls_beta[!(!in_chi_sq & !in_beta),], aes(x=altCount_input/totalCount_input, y =  altCount_IP/totalCount_IP, color=group[!(!in_chi_sq & !in_beta)]))+
  geom_point(aes(color = 'black'), data = bqtls_beta[group == "Not significant",], color="black")+
  geom_point()+
  #lims(x = c(0,1), y = c(0,1))+
geom_abline(slope = 1, intercept = 0, col="red", lty="dashed")+
    labs(x = "Alt Ratio in Input", y = "Alt Ratio in IP", color = "", title = paste0(rbps[j], " | Significant hits of two models both at q < .05"))
print(p)
}
```


## Looking at UNC13A locus (a particular locus interesting to ALS biology)
```{r}
# UNC13A
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  in_unc13a = with(bqtls_beta, (position >= 17601336) & (position <= 17688365))
  cat(rbps[j],'\n')
  cat(sum(in_unc13a), "SNPs in UNC13A made it past filtering\n")
  cat(sum(in_unc13a & in_chi_sq), "SNPs in UNC13A significant by chi-sq model\n")
  cat(sum(in_unc13a & in_beta), "SNPs in UNC13A significant by beta model\n")
  cat("\n-------------------------------------------\n")
}
```


## Looking at read counts for significant hits -- replacing x axis with geometric mean of input and IP totalCount
```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  x=bqtls_beta$totalCount_input
  y=bqtls_beta$totalCount_IP
  #dat <- data.table(totalCount_input = c(x[in_chi_sq], x[in_beta], x[!in_beta & !in_chi_sq]),
  #           totalCount_IP = c(y[in_chi_sq], y[in_beta], y[!in_beta & !in_chi_sq]),
  #           group = rep(c("ChiSq", "Beta", "Neither"), c(sum(in_chi_sq), sum(in_beta), sum(!in_beta & !in_chi_sq))))
  dat <- data.frame(totalCount_input = c(x[in_chi_sq], x[in_beta], x),
             totalCount_IP = c(y[in_chi_sq], y[in_beta], y),
             group = rep(c("ChiSq", "Beta", "Baseline"), c(sum(in_chi_sq), sum(in_beta), nrow(bqtls_beta))))
  p1 <- ggplot(dat,aes(x = totalCount_input, color=group))+
    geom_density()+
    scale_x_log10()+
    labs(title = paste(rbps[j],"| # of reads input"))
  p2 <- ggplot(dat,aes(x = totalCount_IP, color=group))+
    geom_density()+
    scale_x_log10()+
    labs(title = paste(rbps[j],"| # of reads IP"))
  p3 <- ggplot(dat,aes(x = sqrt(totalCount_input*totalCount_IP), color=group))+
    geom_density()+
    scale_x_log10()+
    labs(title = paste(rbps[j],"| geometric mean of # of reads"))
  #print(p1)
  print(p3)
}
```


```{r}
lapply(1:length(bqtls_betas), function(j) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  c(sum(in_chi_sq), sum(in_beta), sum(!in_beta & !in_chi_sq))
}) -> res
x = as.data.frame(Reduce(res, f=rbind))
names(x) = c("ChiSq", "Beta", "Neither")
x
```

## Top hits for beta model

```{r}
lapply(1:length(bqtls_betas), function(j) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  bqtls_beta[in_beta,]
}) -> res

res[[1]]%>%arrange(asb_q)
```


## Top hits for chi-squared model

```{r}
lapply(1:length(bqtls_betas), function(j) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  cbind(bqtls_beta, chisq)[in_chi_sq,]%>%as_tibble
}) -> res

res[[1]]%>%arrange(q.value)
```


```{r}
lapply(1:length(bqtls_betas), function(j) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  c(rbps[j],
    sum(in_chi_sq), 
    sum(in_beta), 
    nrow(bqtls_beta),
    #sum(!in_beta & !in_chi_sq),
    sum(in_chi_sq & bqtls_beta$in_peak),
    sum(in_beta & bqtls_beta$in_peak),
    #sum(!in_beta & !in_chi_sq & bqtls_beta$in_peak),
    sum(bqtls_beta$in_peak),
    sum(in_chi_sq & bqtls_beta$near_peak_100k),
    sum(in_beta & bqtls_beta$near_peak_100k),
    sum(bqtls_beta$near_peak_100k)
    )
}) -> res
x = as.data.frame(Reduce(res, f=rbind))
names(x) = c('rbp',"ChiSq", "Beta", "Everything", "ChiSq In Peak", "Beta In Peak", "Everything In Peak","ChiSq Near Peak", "Beta Near Peak", "Everything Near Peak")
x
```

## qq-plots

```{r}
bqtls_betas[[1]]$asb_q%>%qq(main="Beta ASB q-values")%>%print
all_chisq[[1]]$p.value%>%p.adjust(method='fdr')%>%qq(main = "Chi-Sq q-values")%>%print
```

## Venn diagram of overlap between significant hits of two models in hNIL-control

```{r}
j = 1
bqtls_beta <- bqtls_betas[[j]]
chisq <- all_chisq[[j]]
in_chi_sq <- chisq$q.value < 0.05
in_beta  <- bqtls_beta$asb_q < 0.05

list(chiSq = bqtls_beta$variantID[in_chi_sq],
     beta = bqtls_beta$variantID[in_beta])%>%
venn%>%
plot
```



```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  # I want to know for the chisq data if there are any SNPs that have 0s in the input
  .idx = with(bqtls_beta, in_beta & (altCount_input == 0 | refCount_input == 0))
  print(sum(.idx))
}
```


```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  p = bqtls_beta%>%
    ggplot(aes(x = sort(asb_q), y = sort(ase_q)))+
    geom_point(shape=1, alpha = 0.5)+
    geom_abline(slope = 1, intercept = 0, linetype='dashed', color='red')+
    labs(x = "Allele-Specific Binding q-value (sorted)", y = "Allele-Specific Expression q-value (sorted)",
         title=rbps[j])
  print(p)
  p = bqtls_beta%>%
    ggplot(aes(x = sort(-log10(asb_q)), y = sort(-log10(ase_q))))+
    geom_point(shape=1, alpha=0.5)+
    geom_abline(slope = 1, intercept = 0, linetype='dashed', color='red')+
    labs(x = "Allele-Specific Binding q-value (sorted -log10)", y = "Allele-Specific Expression q-value (sorted -log10)",
         title=rbps[j])
  print(p)
}
```

```{r}

lapply(1:length(bqtls_betas), function(j) {
  bqtls_beta <- bqtls_betas[[j]]
  bqtls_beta$variantID[bqtls_beta$ase_q < .05]
})%>%
`names<-`(rbps)%>%
  venn%>%
  plot(main='ASE significant hits (q < .05) q-value sharing')
```
```{r}
IP_dats <- lapply(1:length(bqtls_betas), function(j) { read_tsv(ip_files[j]) })
```
```{r}
input_files <- c('/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIL-control-tdp/allelic/24a-hNIL-control-tdp_input_allelic.out',
 '/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIL-c9-tdp/allelic/24a-hNIL-c9-tdp_input_allelic.out',
 '/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIP-control-tdp/allelic/24a-hNIP-control-tdp_input_allelic.out',
 '/gpfs/commons/home/dmeyer/bindingQTL_share/24a-hNIP-c9-tdp/allelic/24a-hNIP-c9-tdp_input_allelic.out')
```

```{r}
IP_dats[[1]]
```


```{r}
binom_results <- lapply(1:length(bqtls_betas), function(j) {
  dat <- IP_dats[[j]]%>%filter(variantID %in% readLines("../both_het_snps.txt"), totalCount >= 30)
  binom_res = foreach(i = 1:nrow(dat), .combine = bind_rows) %dopar% {
    res = binom.test(dat$altCount[i],dat$totalCount[i], p=0.5)
    with(res, tibble(statistic, parameter, p.value, conf.int[1], conf.int[2], estimate))
  }
  binom_res
})

saveRDS(binom_results, "binom_results_IP_hets.RDS")

binom_results <- lapply(1:length(bqtls_betas), function(j) {
  dat <- invisible(read_tsv(input_files[j]))%>%filter(variantID %in% readLines("../both_het_snps.txt"), totalCount >= 10)
  binom_res = foreach(i = 1:nrow(dat), .combine = bind_rows) %dopar% {
    res = binom.test(dat$altCount[i],dat$totalCount[i], p=0.5)
    with(res, tibble(statistic, parameter, p.value, conf.int[1], conf.int[2], estimate))
  }
  binom_res
})
saveRDS(binom_results, "binom_results_input_hets.RDS")
```

```{r}
bIn <- readRDS("binom_results_input_hets.RDS")
```


```{r}
binom_results <- lapply(1:length(bqtls_betas), function(j) {
  dat <- IP_dats[[j]]%>%filter(totalCount >= 30)
  binom_res = foreach(i = 1:nrow(dat), .combine = bind_rows) %dopar% {
    res = binom.test(dat$altCount[i],dat$totalCount[i], p=0.5)
    with(res, tibble(statistic, parameter, p.value, conf.int[1], conf.int[2], estimate))
  }
  binom_res
})
saveRDS(binom_results, "binom_results_IP.RDS")

binom_results <- lapply(1:length(bqtls_betas), function(j) {
  dat <- invisible(read_tsv(input_files[j]))%>%filter(totalCount >= 30)
  binom_res = foreach(i = 1:nrow(dat), .combine = bind_rows) %dopar% {
    res = binom.test(dat$altCount[i],dat$totalCount[i], p=0.5)
    with(res, tibble(statistic, parameter, p.value, conf.int[1], conf.int[2], estimate))
  }
  binom_res
})
saveRDS(binom_results, "binom_results_input.RDS")
```

```{r}
registerDoMC(2) # Set number of cores here for parallel processing
j = 1
dat <- IP_dats[[j]]%>%filter(totalCount >= 30)
binom_res = foreach(i = 1:nrow(dat), .combine = bind_rows) %dopar% {
  res = binom.test(dat$altCount[i],dat$totalCount[i], p=0.5)
  with(res, tibble(statistic, parameter, p.value, conf.int[1], conf.int[2], estimate))
}

```
```{r}
input_dats <- lapply(1:length(rbps), function(j) {
  read_tsv(input_files[j])
})
```


```{r}
for (j in 1:length(rbps)) {
  tmp <- cbind(read_tsv(input_files[j])%>%filter(totalCount >= 10, variantID %in% readLines("../both_het_snps.txt")), bIn[[j]])
  bIn[[j]] <- tmp
  #dat <- IP_dats[[j]]%>%filter(variantID %in% readLines("../both_het_snps.txt"), totalCount >= 30)
  #tmp <- cbind(dat, bIP[[j]])
  #bIP[[j]] <- tmp
}

```

```{r}
for (j in 1:length(rbps)) {
  #bIP[[j]]$q.value <- p.adjust(bIP[[j]]$p.value, "fdr")
  bIn[[j]]$q.value <- p.adjust(bIn[[j]]$p.value, "fdr")
}
```


```{r}
saveRDS(bIn, "binom_results_input_hets.RDS")
saveRDS(bIP, "binom_results_IP_hets.RDS")
```


```{r}
bIn <- readRDS("binom_results_input_hets.RDS")
bIP <- readRDS("binom_results_IP_hets.RDS")
```

```{r}
bIP[[4]]%>%filter(variantID %in% c("rs12973192" , "rs12608932"))
```

```{r}
c("rs12973192" , "rs12608932")%in% readLines("../both_het_snps.txt")
```


```{r}
#for (i in 1:length(bIn)) {
#  bIn[[i]] <- bIn[[i]]%>%mutate(rbp=rbps[i])
#  bIP[[i]] <- bIP[[i]]%>%mutate(rbp=rbps[i])
#}
arrow::write_feather(data.table::rbindlist(bIn), "binom_results_input_hets.feather")
arrow::write_feather(data.table::rbindlist(bIP), "binom_results_IP_hets.feather")
```



```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  dat = bqtls_beta%>%inner_join(bIP[[j]]%>%rename(chrom=contig), by = c("chrom", "position", "variantID", "refAllele", "altAllele"))
  dat$q.value <- p.adjust(dat$p.value, "fdr")
  in_binom <- dat$q.value < .05
  stopifnot(all(dat$variantID == bqtls_beta$variantID))
  #dat = bqtls_beta%>%inner_join(bIn[[j]]%>%rename(chrom=contig), by = c("chrom", "position", "variantID", "refAllele", "altAllele"))
  dat = bIn[[j]]
  dat$q.value <- p.adjust(dat$p.value, "fdr")
  in_binom_input <- dat$q.value < .05
  #stopifnot(all(dat$variantID == bqtls_beta$variantID))
  list(
    binom_IP   = bqtls_beta$variantID[in_binom],
    binom_input= dat$variantID[in_binom_input],
    beta       = bqtls_beta$variantID[in_beta],
    #beta_ase      = bqtls_beta$variantID[bqtls_beta$ase_q < .05],
    chisq      = bqtls_beta$variantID[in_chi_sq]
  )%>%venn%>%plot(main = rbps[j])%>%print
}
```
```{r}
for (j in 1:length(bqtls_betas)) {
  bqtls_beta <- bqtls_betas[[j]]
  chisq <- all_chisq[[j]]
  in_chi_sq <- chisq$q.value < 0.05
  in_beta  <- bqtls_beta$asb_q < 0.05
  dat = bqtls_beta%>%inner_join(bIP[[j]]%>%rename(chrom=contig), by = c("chrom", "position", "variantID", "refAllele", "altAllele"))
  dat$q.value <- p.adjust(dat$p.value, "fdr")
  in_binom <- dat$q.value < .05
  stopifnot(all(dat$variantID == bqtls_beta$variantID))
  #dat = bqtls_beta%>%inner_join(bIn[[j]]%>%rename(chrom=contig), by = c("chrom", "position", "variantID", "refAllele", "altAllele"))
  dat = bIn[[j]]
  dat$q.value <- p.adjust(dat$p.value, "fdr")
  in_binom_input <- dat$q.value < .05
  #stopifnot(all(dat$variantID == bqtls_beta$variantID))
  list(
    binom_IP   = bqtls_beta$variantID[in_binom],
    binom_input= dat$variantID[in_binom_input],
    beta       = bqtls_beta$variantID[in_beta],
    beta_ase      = bqtls_beta$variantID[bqtls_beta$ase_q < .05]
    #chisq      = bqtls_beta$variantID[in_chi_sq]
  )%>%venn%>%plot(main = rbps[j], fill = c(7,2,3,5))%>%print
}
```

```{r}
binom_results_files <- paste0(dirname(filtered_input_files),'/', rbps, '_binomresults.txt')
for (j in 1:length(rbps)) {
  bIn[[j]]%>%inner_join(bIP[[j]], by = c("contig", "position", "variantID", "refAllele", "altAllele"), suffix = c("_input", "_IP"))%>%
    rename(chrom=contig)%>%
    mutate(
      q.value_input = p.adjust(p.value_input, 'fdr'),
      q.value_IP = p.adjust(p.value_IP, 'fdr'))%>%
    write_tsv(binom_results_files[j])
}
cat(paste0('[', paste(paste0('"', binom_results_files, '"'), collapse=",\n"), ']'))
```

```{r}
j = 1
bIn[[j]]%>%inner_join(bIP[[j]], by = c("contig", "position", "variantID", "refAllele", "altAllele"), suffix = c("_input", "_IP"))%>%
  rename(chrom=contig)%>%
  mutate(
    q.value_input = p.adjust(p.value_input, 'fdr'),
    q.value_IP = p.adjust(p.value_IP, 'fdr'))%>%
  filter(variantID == "rs113951577")
```

```{r}
"[ACGT][ACGT]+"
```

